Czech parliament meeting recordings as ASR training data

### 2020-04-13 2020-tsd-brno-svolocz/svolocz.tex
proof reading of svolocz

The predicted transcript and the stenographic one have then been compared for
Levenshtein distance, determining the edit operations needed to transform one
into the other. For each predicted word, an un-reliability score is then
computed as the number of edit operations taken on it divided by its length.
A reliability score is actually used, as 1 - un-reliability.
Figure~\ref{fig:align} shows how the stenographic transcript is aligned with the
audio on word level.

@@

The problem of selecting the optimal set of silences so that the longest ones
are kept and split the recording in chunks of set length boundaries looks like
one for dynamic programming but I use a simpler approach: Start with a set of
all silences predicted by the forced alignment. Iterate over the silences
shortest-first and remove it if it doesn't break the constraints.

@@

Minimum reliability of border tokens is considered to minimize the danger of
false alignment. Mean reliability is considered because it is OK for some
words to have reliability zero: there are enough errors in the prediction,
that's why we use the manual transcript after all. But if too many tokens have
too low reliability, then it is a sign of a suspicious segment. The number of
words has a minimum because with only a few words, the probability of
misalignment with good score is much greater than when there are enough words.

Why use mean reliability and not median? The way the reliability is computed,
considers the number of edit operations on one line in the automatic transcript.
In the case where there are many insertions, the reliability of one line can go
arbitrarily deep sub zero. So it can happen that there are several lines
extra words in the (mis)aligned chunk. The mean taps these.

@@

>>>>

The predicted transcript and the stenographic one have then been compared for
Levenshtein distance, determining the edit operations needed to transform one
into the other. For each predicted word, a reliability score is then
computed as 1 - unreliability where unreliability is the number of edit
operations taken on it divided by its length.
Figure~\ref{fig:align} shows how the stenographic transcript is aligned with the
audio on word level.

@@

The problem of selecting the optimal set of silences so that the longest ones
are kept and split the recording in chunks of set length boundaries looks like
one for dynamic programming but a simpler approach is also possible: Start with a set of
all silences predicted by the forced alignment. Iterate over the silences
shortest-first and remove it if it doesn't break the constraints.

@@

Minimum reliability of border tokens is considered to minimize the danger of
shifted alignment boundaries. Mean reliability is considered because it is OK for some
words to have reliability zero: there are enough errors in the prediction,
that's why we use the manual transcript after all. But if too many tokens have
too low reliability, then it is a sign of a suspicious segment. The number of
words has a minimum because with only a few words, the probability of
misalignment with good score is much greater than when there are enough words.

Why use mean reliability and not median? The way the reliability is computed
considers the number of edit operations on one line in the automatic transcript.
In the case where there are many insertions, the reliability of one line can go
arbitrarily deep sub zero. So it can happen that there are several inserted
words in a (mis)aligned chunk that only affect the reliability score of a single
word. The mean taps these while the median doesn't.

@@

Source code for scraping and building the corpus is in public domain and
available on \texttt{GitHub.com/Sixtease/cz-parliament-speech-corpus}.
